KidsAIR: covariate associations exposure analysis

### 2020-04-30 ambient_summary.Rmd
ambient temp/pm and exposure model udpates

```{r}
exposure_analysis_data_long <- read_rds("Output/exposure_analysis_data_long_new.rds")

exposure_analysis_data_medium <- read_rds("Output/exposure_analysis_data_medium.rds")

exposure_analysis_data_short <- read_rds("Output/exposure_analysis_data_short.rds")

sums_rolling_pm_data <- read_rds("Output/sums_rolling_pm_data.rds")

health_exposure_data_sampling_day <- read_rds("Output/health_exposure_data_sampling_day.rds")
```

@@

wmt_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "WMT") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    theme_void() +
    labs(title = "WMT mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = EPA monitors",
         fill = "Ambient PM", size = "Ambient PM") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 8)
wmt_plot
```

```{r}
nn_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "NN") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "NN mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = EPA monitors",
         fill = "Ambient PM", size = "Ambient PM") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 1.5)
nn_plot
```

```{r}
ak_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "AK") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 5, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "AK mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangle = EPA monitor",
         fill = "Ambient PM", size = "Ambient PM") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 6)
ak_plot
```

@@

wmt_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "WMT") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    theme_void() +
    labs(title = "WMT mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations",
         fill = "Ambient temp", size = "Ambient temp") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 20)
wmt_plot
```

```{r}
nn_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "NN") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "NN mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations",
         fill = "Ambient temp", size = "Ambient temp") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 45)
nn_plot
```

```{r}
ak_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "AK") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 5, fill = "yellow",
               color = "black") +
    geom_point(aes(long_zip, lat_zip, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "AK mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations",
         fill = "Ambient temp", size = "Ambient temp") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 30)
ak_plot
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/KidsAIR/")

exposure_analysis_data_long <- 
  read_rds(paste0(file_path, "Output/exposure_analysis_data_long_new.rds"))

exposure_analysis_data_medium <- 
  read_rds(paste0(file_path, "Output/exposure_analysis_data_medium.rds"))

exposure_analysis_data_short <- 
  read_rds(paste0(file_path, "Output/exposure_analysis_data_short.rds"))

sums_rolling_pm_data <- 
  read_rds(paste0(file_path, "Output/sums_rolling_pm_data.rds"))

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds"))
```

@@

wmt_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "WMT") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_home, lat_home, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    theme_void() +
    labs(title = "WMT mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = EPA monitors",
         fill = "Ambient PM", size = "Ambient PM") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 8)
wmt_plot
```

```{r}
nn_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "NN") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    geom_point(aes(long_home, lat_home, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "NN mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = EPA monitors",
         fill = "Ambient PM", size = "Ambient PM") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 1.5)
nn_plot
```

```{r}
ak_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "AK") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_pm = mean(amb_pm_24hr, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_pm, lat_pm), shape = 24, size = 5, fill = "yellow",
               color = "black") +
    geom_point(aes(long_home, lat_home, fill = mean_amb_pm, size = mean_amb_pm), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "AK mean ambient PM at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangle = EPA monitor",
         fill = "Ambient PM", size = "Ambient PM") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 6)
ak_plot
```

@@

wmt_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "WMT") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=wmt_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_home, lat_home, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    theme_void() +
    labs(title = "WMT mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations",
         fill = "Ambient temp", size = "Ambient temp") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 20)
wmt_plot
```

```{r}
nn_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "NN") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=nn_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 3, fill = "yellow",
               color = "black") +
    geom_point(aes(long_home, lat_home, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "NN mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations",
         fill = "Ambient temp", size = "Ambient temp") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 45)
nn_plot
```

```{r}
ak_plot <- exposure_analysis_data_medium %>%
  ungroup() %>% 
  filter(area == "AK") %>% 
  group_by(zip) %>% 
  mutate(mean_amb_temp = mean(mean_temp, na.rm = TRUE)) %>% 
  distinct(zip, .keep_all = TRUE) %>% 
  filter(!is.na(zip)) %>% 
  ggplot() +
    geom_polygon(data=ak_map, aes(x=long, y=lat, group=group), 
               color="black", fill = "azure", size = 1.2) +
    geom_point(aes(long_temp, lat_temp), shape = 24, size = 5, fill = "yellow",
               color = "black") +
    geom_point(aes(long_home, lat_home, fill = mean_amb_temp, size = mean_amb_temp), 
               shape = 21, color = "black") +
    theme_void() +
    labs(title = "AK mean ambient Temp at each zipcode during indoor PM sampling",
         subtitle = "Yellow triangles = weather stations",
         fill = "Ambient temp", size = "Ambient temp") +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 30)
ak_plot
```

### 2020-04-30 collinearity_exposure_analysis.Rmd
ambient temp/pm and exposure model udpates

####### Format ambient data to merge with analysis data below
ambient_data <- exposure_analysis_data_long %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  #filter(area == "AK") %>% 
  filter(!is.na(sampling_day)) %>% 
  filter(!is.na(sample_date)) %>%
  select(area, home, child_id_char, sample_date, sampling_day, pm_mean_daily,
         zip:mean_temp_roll_4day) %>% 
  group_by(home) %>% 
  mutate(amb_pm_sampling_period_5 = mean(amb_pm_24hr, na.rm = TRUE)/5,
         mean_temp_sampling_period_5 = mean(mean_temp, na.rm = TRUE)/5) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup()

>>>>

####### Format ambient data to merge with analysis data below
ambient_data <- exposure_analysis_data_long %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  #filter(area == "AK") %>% 
  filter(!is.na(sampling_day)) %>% 
  filter(!is.na(sample_date)) %>%
  select(area, home, child_id_char, sample_date, sampling_day, pm_mean_daily,
         amb_pm_24hr:mean_temp_roll_4day) %>% 
  group_by(home) %>% 
  mutate(amb_pm_sampling_period_5 = mean(amb_pm_24hr, na.rm = TRUE)/5,
         mean_temp_sampling_period_5 = mean(mean_temp, na.rm = TRUE)/5) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup()

### 2020-04-30 exposure_covariate_associations.Rmd
ambient temp/pm and exposure model udpates

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  left_join(sums_temp_change, by = c("area", "home")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home"))

@@

  tidy_results <<- tidy(analysis_results) %>% 
    filter(term != '(Intercept)') %>% 
    mutate(estimate = round(estimate, digits = 2),
           'p-value' = round(p.value, digits = 2),
           term = gsub("analysis_covar", paste0(label, ": "), term)) %>% 
    select(term, estimate, 'p-value')

@@

d39 <- analysis_function("sums_mean_sampling_period_5", "SUMs mean temperature")
d40 <- analysis_function("temp_perc_25_2level", "SUMs - % obs > 25 degrees C")
d41 <- analysis_function("temp_perc_27_2level", "SUMs - % obs > 27 degrees C")
d42 <- analysis_function("temp_perc_30_2level", "SUMs - % obs > 30 degrees C")
d43 <- analysis_function("sums_events_sampling_period", 
                         "Mean daily SUMs events - 5+ degree C temp increase in 20 min")

@@

d46 <- analysis_function("home_act_gas", "Home activity - gas appliance")
d47 <- analysis_function("home_act_elect", "Home activity - electric appliance")
d48 <- analysis_function("home_act_propane", "Home activity - propane appliance")
d49 <- analysis_function("home_act_oil", "Home activity - oil appliance")
d50 <- analysis_function("home_act_other", "Home activity - other appliance")
d51 <- analysis_function("home_act_smoking", "Home activity - smoking")
d52 <- analysis_function("home_act_incense", "Home activity - incense")
d53 <- analysis_function("home_act_candle", "Home activity - candle")
d54 <- analysis_function("home_act_windows", "Home activity - windows open")
d55 <- analysis_function("home_act_door", "Home activity - doors open")
d56 <- analysis_function("home_act_sweep", "Home activity - cleaning")

d57 <- analysis_function("stove_grade_3level", "Stove grade")

####### Combine results to use in a table
table_data <- rbind(d1, d2, d3, d4, d5, d6,
                    d7, d8, d9, d10, d11, d12, d13, d14, d15, d16, d17, d18,
                    d19, d20, d21, d22,
                    d23, d24, d25, d26,
                    d27, d28, d29, d30,
                    d31, d32, d33, d34, d35, d36, d37, d38,
                    d39, d40, d41, d42, d43,
                    d44, d45,
                    d46, d47, d48, d49, d50, d51, d52, d53, d54, d55, d56,
                    d57)

####### Print full table of results
kable(table_data, longtable = TRUE,
      caption = "Indoor PM2.5 (natural log transformed) and covariate associations") %>% 
   kable_styling(latex_options = "repeat_header") %>% 
   row_spec(0, bold = TRUE) %>% 
   pack_rows("Demographic variables", 1, 8) %>%
   pack_rows("Home characteristics", 9, 31) %>%
   pack_rows("Stove use", 32, 36) %>%
   pack_rows("Wood moisture content", 37, 40) %>%
   pack_rows("Indoor temperature and relative humidity", 41, 48) %>%
   pack_rows("Stove Use Monitors (SUMs) temperature", 49, 53) %>%
   pack_rows("Ambient data", 54, 55) %>%
   pack_rows("Home activities - Sum of all sampling days", 56, 66) %>%
   pack_rows("Stove grade", 67, 68) %>%
   footnote(c("PM2.5 = fine particulate matter", 
              "PM2.5 and all covariates have been averaged or summed to produce 1 observation per sampling period"))
```

>>>>

####### Format full data to use for analysis
analysis_data <- exposure_analysis_data_short %>% 
  filter(winter_id == 1 & treatment == "Placebo" & area == "WMT") %>% 
  group_by(area, home) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  ungroup() %>% 
  mutate(moisture_closest_2level = cut(moisture_closest, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE),
         moisture_winter_2level = cut(mean_moisture_winter, breaks = c(0, 10.5, 100),
                                 labels = c("<10.5", "10.5+"),
                                 right = FALSE)) %>% 
  mutate(temp_max_2level = cut(temp_indoor_max, breaks = c(0, 30, 100),
                                 labels = c("<30", "30+"),
                                 right = FALSE),
         temp_min_2level = cut(temp_indoor_min, breaks = c(0, 16.5, 100),
                                 labels = c("<16.5", "16.5+"),
                                 right = FALSE),
         rh_max_2level = cut(rh_indoor_max, breaks = c(0, 40, 100),
                                 labels = c("<40", "40+"),
                                 right = FALSE),
         rh_min_2level = cut(rh_indoor_min, breaks = c(0, 20, 100),
                                 labels = c("<20", "20+"),
                                 right = FALSE)) %>% 
  mutate(sums_mean_sampling_period_5 = sums_mean_sampling_period/5,
         temp_perc_25_2level = cut(temp_perc_25, breaks = c(0, 50, 100),
                                 labels = c("<50", "50+"),
                                 right = FALSE),
         temp_perc_27_2level = cut(temp_perc_27, breaks = c(0, 35, 100),
                                 labels = c("<35", "35+"),
                                 right = FALSE),
         temp_perc_30_2level = cut(temp_perc_30, breaks = c(0, 10, 100),
                                 labels = c("<10", "10+"),
                                 right = FALSE)) %>% 
  left_join(sums_temp_change, by = c("area", "home")) %>% 
  left_join(ambient_data, by = c("area", "home")) %>% 
  select(-starts_with("home_act")) %>% 
  left_join(home_activity_data, by = c("area", "home")) %>% 
  mutate(home_act_door_2level = cut(home_act_door, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_smoke_2level = cut(home_act_smoking, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_windows_2level = cut(home_act_windows, breaks = c(0, 1, 7),
                                 labels = c("<1", "1+"),
                                 right = FALSE),
         home_act_sweep_2level = cut(home_act_sweep, breaks = c(0, 3, 7),
                                 labels = c("<3", "3+"),
                                 right = FALSE))

@@

  tidy_results <<- tidy(analysis_results, conf.int = TRUE) %>% 
    filter(term != '(Intercept)') %>% 
    mutate(Estimate = round(estimate, digits = 2),
           'P-value' = round(p.value, digits = 2),
           'Upper 95% CL' = round(conf.high, digits = 2),
           'Lower 95% CL' = round(conf.low, digits = 2),
           Term = gsub("analysis_covar", paste0(label, ": "), term)) %>% 
    select(Term, Estimate, 'Lower 95% CL', 'Upper 95% CL', 'P-value')

@@

d39 <- analysis_function("sums_mean_sampling_period_5", "SUMs mean temperature")
d40 <- analysis_function("temp_perc_25_2level", "SUMs - % obs > 25 degrees C")
d41 <- analysis_function("temp_perc_27_2level", "SUMs - % obs > 27 degrees C")
d42 <- analysis_function("temp_perc_30_2level", "SUMs - % obs > 30 degrees C")
d43 <- analysis_function("sums_events_sampling_period", 
                         "Daily SUMs events - 5C temp increase in 20 min")

@@

d46 <- analysis_function("home_act_gas", "Home activity - gas appliance")
d47 <- analysis_function("home_act_elect", "Home activity - electric appliance")
d48 <- analysis_function("home_act_propane", "Home activity - propane appliance")
d49 <- analysis_function("home_act_oil", "Home activity - oil appliance")
d50 <- analysis_function("home_act_other", "Home activity - other appliance")
d51 <- analysis_function("home_act_smoking", "Home activity - smoking")
d52 <- analysis_function("home_act_incense", "Home activity - incense")
d53 <- analysis_function("home_act_candle", "Home activity - candle")
d54 <- analysis_function("home_act_windows", "Home activity - windows open")
d55 <- analysis_function("home_act_door", "Home activity - doors open")
d56 <- analysis_function("home_act_sweep", "Home activity - cleaning")
d57 <- analysis_function("home_act_smoke_2level", "Home activity - smoking 2 level")
d58 <- analysis_function("home_act_windows_2level", "Home activity - windows 2 level")
d59 <- analysis_function("home_act_door_2level", "Home activity - doors 2 level")
d60 <- analysis_function("home_act_sweep_2level", "Home activity - cleaning 2 level")

d61 <- analysis_function("stove_grade_3level", "Stove grade")

####### Combine results to use in a table
table_data <- rbind(d1, d2, d3, d4, d5, d6,
                    d7, d8, d9, d10, d11, d12, d13, d14, d15, d16, d17, d18,
                    d19, d20, d21, d22,
                    d23, d24, d25, d26,
                    d27, d28, d29, d30,
                    d31, d32, d33, d34, d35, d36, d37, d38,
                    d39, d40, d41, d42, d43,
                    d44, d45,
                    d46, d47, d48, d49, d50, d51, d52, d53, d54, d55, d56,
                    d57, d58, d59, d60,
                    d61)

####### Print full table of results
kable(table_data, longtable = TRUE,
      caption = "Indoor PM2.5 (natural log transformed) and covariate associations") %>% 
   kable_styling(latex_options = "repeat_header") %>% 
   row_spec(0, bold = TRUE) %>% 
   pack_rows("Demographic variables", 1, 8) %>%
   pack_rows("Home characteristics", 9, 31) %>%
   pack_rows("Stove use", 32, 36) %>%
   pack_rows("Wood moisture content", 37, 40) %>%
   pack_rows("Indoor temperature and relative humidity", 41, 48) %>%
   pack_rows("Stove Use Monitors (SUMs) temperature", 49, 53) %>%
   pack_rows("Ambient data", 54, 55) %>%
   pack_rows("Home activities - Sum of all sampling days", 56, 69) %>%
   pack_rows("Stove grade", 70, 71) %>%
   footnote(c("PM2.5 = fine particulate matter", 
              "PM2.5 and all covariates have been averaged or summed to produce 1 observation per sampling period"))
```
